---
title: "p8105_hw5"
author: "Hao Sun"
date: "11/1/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Problem 1

The code chunk below loads the iris dataset from the tidyverse package and introduces some missing values in each column. The purpose of this problem is to fill in those missing values.
```{r Creat problem dataset}
set.seed(10)
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

There are two cases to address:

For numeric variables, you should fill in missing values with the mean of non-missing values
For character variables, you should fill in missing values with "virginica"
Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement.


```{r PB1 }

fill_NA = function(vector){
   if (class(vector) == "numeric") {
     ###missing values as the mean of non-missing values 
  coalesce(vector,round(mean(vector[!is.na(vector)]),digit = 1))
  }

  else if (class(vector) == "character") {
  #### fill in missing values with "virginica" 
    coalesce(vector,"virginica")
  }
  else 
 stop("Input shall be either numeric or character vector")
}

##Do everything across column and merge the output into dataset.
iris_without_missing<-map_df(iris_with_missing,fill_NA)

iris_without_missing
```

This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help

```{r Pb 2}
##Function definition:
read_and_label<-function(filename){
   if (class(filename) == "character") {
     path = str_c("./data/",filename)
     read_csv(path)%>%mutate(arm_id = str_replace(filename,".csv", " "))
  }
  else 
 stop("Input shall be character")
}

file_list<-list.files("./data")
weekly_obs<-map_df(file_list,read_and_label)%>%
  separate(arm_id, into = c("arm", "subject_id"), sep = "_") %>%
  pivot_longer(names_to = "weeks", values_to = "obs", cols = week_1:week_8 )%>%
  mutate(arm = as.factor(arm), weeks = as.factor(weeks))

weekly_obs%>%
  ggplot(aes(x = as.numeric(weeks),y = obs,color = subject_id))+
  geom_line()+
  facet_grid(. ~ arm)


```

Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.



